\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2013-04-25 doc/sw-system.tex
First beta results circulated

We perform a ``Pseudo-online'' analysis of the classifications, 
updating a probabilistic model of every (anonymous) volunteer's
expertise, and every subject (in both the training and test sets), on a
daily basis. This allows us to track the speed with which the crowd
learns about lenses, and also gives us a dynamic estimate of the
posterior probability for  any given  subject being a lens, given all
classifications of it. Assigning thresholds in this lens probability
allows us to make good decisions about whether or not to accept a
subject into the collection of candidates visible in \Talk, and also
whether or not to  carry on classifying a subject at all.

@@

Indeed, the information content of each classification can be estimated by an
agent before the next classification is made, just from its confusion matrix.
We define the expected information per classification, or {\it expertise}, as
\be
  \langle I_k \rangle = \frac{1}{2} 
                        \sum_{i} \left( \mathcal{M}^k_{i}  
              + \mathcal{M}^k_{i}\cdot\log_2{\mathcal{M}^k_i} \right),
  \label{eq:app:info}
\ee
where $i$ runs over all 4 elements of the confusion matrix 
$\mathcal{M}^k_i$, and $\langle I_k \rangle$ is measured in ``bits.'' 
The second term in the sum is recognisable as a
negative entropy, while the first term and the factor of 1/2
account for the way the confusion matrix encodes the results for the
classification of two types of subject, and that the probabilities
associated with each type are normalised. \Eref{eq:app:info} gives the
required result, that 
both the hypothetical {\it perfect} and
{\it obtuse} classifiers contribute 
1 bit of information each, per classification.

>>>>

We perform a ``Pseudo-online'' analysis of the classifications, 
updating a probabilistic model of every (anonymous) volunteer's
data, and also updating the lens probability of each subject 
(in both the training and test sets), on a
daily(??) basis. This allows us to track the speed with which the crowd
learns about lenses, and also gives us a dynamic estimate of the
posterior probability for  any given  subject being a lens, given all
classifications of it. Assigning thresholds in this lens probability
allows us to make good decisions about whether or not to accept a
subject into the collection of candidates visible in \Talk, and also
whether or not to  carry on classifying a subject at all.

@@

Indeed, the information content of each classification can be estimated by an
agent before the next classification is made, just from its confusion matrix.
We define the expected contributed information per classification, as
\be
  \langle I_k \rangle = \frac{1}{2} 
                        \sum_{i} \left( \mathcal{M}^k_{i}  
              + \mathcal{M}^k_{i}\cdot\log_2{\mathcal{M}^k_i} \right),
  \label{eq:app:info}
\ee
where $i$ runs over all 4 elements of the confusion matrix 
$\mathcal{M}^k_i$, and $\langle I_k \rangle$ is measured in ``bits.'' 
The second term in the sum is recognisable as a
negative entropy, while the first term and the factor of 1/2
account for the way the confusion matrix encodes the results for the
classification of two types of subject, and that the probabilities
associated with each type are normalised. \Eref{eq:app:info} gives the
required result, that 
both the hypothetical {\it perfect} and
{\it obtuse} classifiers contribute 
1 bit of information each, per classification.
